Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-11-30 MDPI_submission.Rmd
Commit 2023-11-30 07:10

## create local citations file and links here
source("~/CODE/FUNCTIONS/R/gather_citations.R")
suppressMessages(
    gather_citations(
        sourcefile   = "./Article.Rmd",
        mainreposit  = "./Mainreferences.bib",
        localreposit = "./references.bib",
        folderlink   = "./References_links",
        workingdir   = "./"
    )
)
```

@@

TSI$cor.null_value     <- NULL
TSI$cor.alternative    <- NULL
TSI$cor.method         <- NULL
TSI$cor.data_name      <- NULL
TSI$cor.p              <- NULL
TSI$conf.level         <- NULL
care <- grep("^cor\\.", names(TSI), value = T)
for (an in care) {
    TSI[, (an) := NULL ]
}

@@

LT$cor.df           <- NULL
LT$cor.null_value   <- NULL
LT$cor.alternative  <- NULL
LT$cor.method       <- NULL
LT$cor.data_name    <- NULL
LT$cor.p            <- NULL
LT$conf.level       <- NULL
LT$cor.conf_int_1   <- NULL
LT$cor.conf_int_2   <- NULL

>>>>

## create local citations file and links here
source("~/CODE/FUNCTIONS/R/gather_citations.R")
suppressMessages(
    gather_citations(
        sourcefile   = "./Article.Rmd",
        mainreposit  = "./Mainreferences.bib",
        localreposit = "./references.bib",
        folderlink   = "./References_links",
        workingdir   = "./"
    )
)

knit_hooks$set(extrawide = function(before, options, envir) {
    if (before) {
        return("\\begin{adjustwidth}{-\extralength}{0cm}")
    }

    if (!before) {
        return("\\end{adjustwidth}")
    }

    # else {
    #     
    #     output <- vector(mode = "character", length = options$fig.num + 1)
    #     
    #     for (i in 1:options$fig.num) {
    #         output[i] <- sprintf("\\includegraphics{%s}", fig_path(number = i))
    #     }
    #     
    #     output[i+1] <- "\\end{adjustwidth}"
    #     return(paste(output, collapse = ""))
    # }
})

@@

# TSI$cor.null_value     <- NULL
# TSI$cor.alternative    <- NULL
# TSI$cor.method         <- NULL
# TSI$cor.data_name      <- NULL
# TSI$cor.p              <- NULL
TSI$conf.level         <- NULL
care <- grep("^cor\\.", names(TSI), value = T)
for (an in care) {
    TSI[, (an) := NULL ]
}

@@

LT$cor.df           <- NULL
# LT$cor.null_value   <- NULL
# LT$cor.alternative  <- NULL
# LT$cor.method       <- NULL
# LT$cor.data_name    <- NULL
# LT$cor.p            <- NULL
LT$conf.level       <- NULL
LT$cor.conf_int_1   <- NULL
LT$cor.conf_int_2   <- NULL
